---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# costmisc

<!-- badges: start -->
[![technomics: costverse](https://img.shields.io/badge/technomics-costverse-EAC435.svg)](https://github.com/technomics)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![R build status](https://github.com/Technomics/costmisc/workflows/R-CMD-check/badge.svg)](https://github.com/Technomics/costmisc/actions)
[![version: 0.7.4](https://img.shields.io/badge/version-0.7.4-blue.svg)]()
[![coverage: 24.5%25](https://img.shields.io/badge/coverage-24.5%25-red.svg)](https://cran.r-project.org/web/packages/covr/vignettes/how_it_works.html)
<!-- badges: end -->

The package costmisc adds miscellaneous functions to the costverse that support various other packages.

Check out the [pkgdown](https://technomics.github.io/costmisc/) site to browse the features!

If you find a bug or have an idea for a new feature, please use the [issue board](https://github.com/Technomics/costmisc/issues).

## Welcome to the costverse!

The *costverse* is a collection of R packages, inspired by the *tidyverse*. The goal is to create a cohesive ecosystem of R packages to streamline tasks encountered by analysts in the cost analysis profession. This can range from importing common data formats, working with difficult data structures (e.g., a WBS), or applying more advanced analytical techniques!

The *costverse* began as an internal [Technomics](https://www.technomics.net/) project to develop a set of tools that enable our employee owners to solve our clients’ problems more effectively. While aspects of the project remain internal, the following packages are currently available to the public. You are free to use them under the [GPLv3](https://www.gnu.org/licenses/gpl-3.0.en.html) - all that we ask is to please cite us as the authors.

 - [costmisc](https://github.com/Technomics/costmisc/)
 - [readflexfile](https://github.com/Technomics/readflexfile/)

Do not hesitate to contact us if you have questions about what else is in the works!

## Installation

The stable version can be installed directly from the Technomics repository.

```{r eval=FALSE}
install.packages("costmisc", repos = "https://technomics.github.io/repo/")
```

### Development version

To get a bug fix, or to use a feature from the development version, you can install costmisc using the following. 

First install the package devtools if you haven't already.

```{r eval=FALSE}
#install.packages("devtools")

devtools::dev_mode(on = TRUE)
devtools::install_github("Technomics/costmisc")
```
